Deploying and Sharing QSAR Models using Predictive Modeling Markup Language

### 2014-12-03 paper.tex
Added model pseudocode vs. model application code example

>>>>

Excerpt from a Random Forest model in PMML pseudocode representation:
\begin{verbatim}
<TreeModel splitCharacteristic="binarySplit">
  <Node id="1">
    <True/>
    <Node id="2">
      <SimplePredicate field="logP" operator="lessOrEqual" value="3.5"/>
      <!-- More child nodes -->
    </Node>
    <Node id="3">
      <SimplePredicate field="logP" operator="greaterThan" value="3.5"/>
      <!-- More child nodes -->
    </Node>
  </Node>
</TreeModel>
\end{verbatim}

The same in Java application code (using JPMML-Evaluator API) representation:
\begin{verbatim}
FieldValue logP = ExpressionUtil.evaluate(new FieldName("logP"), context);
if(logP.compareToString("3.5") <= 0){ // Node 2
  // More child if-else statements
} else { // Node 3
  // More child if-else statements
}
\end{verbatim}
